---
title: "PHD: Read Aggregate & Merge for Train & Test data sets"
author: "Batch39: 1843 - Gayathri Eshwarappa"
date: "Jul 2018"
output:
  html_document:
    toc: yes
    toc_float: yes
---

# Read Aggregate Merge Weather data with Train & Test data

## Read and Understand data
* Read Train & Test data provided as trainDT & testDT
* Read AllStationsData provided as allStaionDT
* Iteratively read & merge files in 2004 folder as
    1. trainWeatherDT if fileName contains "hourly"
    2. trainPrecipDT if fileName contains  "hdp"

```{r}
weatherDataPath <- "./DataFiles/weatherdata"
fileNames <- dir(weatherDataPath, full.names=T, recursive=T, all.files=T)

trainDT <- fread(input="./DataFiles/Train.csv", sep=',', header=TRUE, na.strings=c("", " ", NA, "NA"))
testDT <- fread(input="./DataFiles/Test.csv", sep=',', header=TRUE, na.strings=c("", " ", NA, "NA"))

# Creating a copy of test Flightnumbers required for creating submission file.
testFlightNumber <- testDT[, .(FlightNumber)]

allStaionDT <- UDFReadWeatherData(fileNames, 'AllStationsData', NA, '|')
trainWeatherDT <- UDFReadWeatherData(fileNames, '2004', 'hourly', ',')
trainPrecipDT <- UDFReadWeatherData(fileNames, '2004', 'hpd', ',')
testWeatherDT <- UDFReadWeatherData(fileNames, '2005', 'hourly', ',')
testPrecipDT <- UDFReadWeatherData(fileNames, '2005', 'hpd', ',')

rm(weatherDataPath, fileNames)
```

**Verify if train & test weather data are loaded correctly**

```{r}
toString(unique(trainWeatherDT[, .(substr(YearMonthDay, 1, 4))])) # Train Weather data should only have 2004 
toString(unique(trainPrecipDT[, .(substr(YearMonthDay, 1, 4))])) # Train precipitation data should only have 2004 
toString(unique(testWeatherDT[, .(substr(YearMonthDay, 1, 4))])) # Test Weather should only have 2004
toString(unique(testPrecipDT[, .(substr(YearMonthDay, 1, 4))])) # Test precipitation data should only have 2004

```

**Convert date columns to appropriate datetime objects using lubridate package**
```{r}
trainWeatherDT[, RecordedDateTime := UDFMakeDateTimeFromString(YearMonthDay, Time)]
testWeatherDT[, RecordedDateTime := UDFMakeDateTimeFromString(YearMonthDay, Time)]
trainPrecipDT[, RecordedDateTime := UDFMakeDateTimeFromString(YearMonthDay, Time)]
testPrecipDT[, RecordedDateTime := UDFMakeDateTimeFromString(YearMonthDay, Time)]

trainDT[, ScheduledDepDateTime := UDFMakeDateTimeFromIndComponents(Year, Month, DayofMonth, ScheduledDepTime)]
trainDT[, ScheduledArrDateTime := UDFMakeDateTimeFromIndComponents(Year, Month, DayofMonth, ScheduledArrTime)]
trainDT[, ActualArrDateTime := dmy_hm(ActualArrivalTimeStamp)]

testDT[, ScheduledDepDateTime := UDFMakeDateTimeFromIndComponents(Year, Month, DayofMonth, ScheduledDepTime)]
testDT[, ScheduledArrDateTime := UDFMakeDateTimeFromIndComponents(Year, Month, DayofMonth, ScheduledArrTime)]


# Drop notRequired columns from DT
trainWeatherDT[, c("YearMonthDay", "Time") := NULL]
testWeatherDT[, c("YearMonthDay", "Time") := NULL]
trainPrecipDT[, c("YearMonthDay", "Time") := NULL]
testPrecipDT[, c("YearMonthDay", "Time") := NULL]

trainDT[, c("Year", "ScheduledDepTime", "ScheduledArrTime", "ActualArrivalTimeStamp") := NULL]
testDT[, c("Year", "ScheduledDepTime", "ScheduledArrTime") := NULL]

```


**Adding new datetime column RecordedTimeToNearestHour, which is rounding recorded time to nearest hour**
```{r}

roundBy <- "12 hours"

trainWeatherDT[, RecordedTimeToNearestHour := round_date(RecordedDateTime, unit=roundBy)]
testWeatherDT[, RecordedTimeToNearestHour := round_date(RecordedDateTime, unit=roundBy)]

trainPrecipDT[, RecordedTimeToNearestHour := round_date(RecordedDateTime, unit=roundBy)]
testPrecipDT[, RecordedTimeToNearestHour := round_date(RecordedDateTime, unit=roundBy)]

trainDT[, RecordedTimeToNearestHour_ORG := round_date(ScheduledDepDateTime, unit=roundBy)]
testDT[, RecordedTimeToNearestHour_ORG := round_date(ScheduledDepDateTime, unit=roundBy)]

trainDT[, RecordedTimeToNearestHour_DST := round_date(ScheduledArrDateTime, unit=roundBy)]
testDT[, RecordedTimeToNearestHour_DST := round_date(ScheduledArrDateTime, unit=roundBy)]
```


##Derive target variable FlightDelayStatus in Train Data

**Take difference of converted  ScheduledArrDateTime & ActualArrDateTime in minutes. If difference in minutes > 15 then FlightDelayStatus is Yes, else No**
```{r}
trainDT[, FlightDelayInMins := round(difftime(ymd_hms(ActualArrDateTime), ymd_hms(ScheduledArrDateTime),  unit="mins"), 0)]
trainDT[, FlightDelayStatus := ifelse(FlightDelayInMins > 15, "Yes", "No")]

trainDT[, c("ActualArrDateTime", "FlightDelayInMins") := NULL]

#Check count of Flight Delay Status
table(trainDT$FlightDelayStatus)

```


## Merge All station data to train & test Data tables
First let us Convert All Station data to appropriate types as per details provided in Attribute_Information.pdf

* TimeZone is numeric values which when added to Local standard time gives quivalent GMT 
* Few rows in TimeZone has character values as explained below
* Alaska-Hawaii timezone = -10 from UTC Standard 
* Bering Standard timezone = 11 from UTC Standard
* Eastern Standard timezone = -5 from UTC Standard
* Yukon Standard timezone = -9 from UTC Standard
```{r}
allStaionDT[TimeZone == "Alaska-Hawaii", TimeZone := "-10" ]
allStaionDT[TimeZone == "Bering Standard", TimeZone := "+10" ]
allStaionDT[TimeZone == "Eastern Standard", TimeZone := "-5" ]
allStaionDT[TimeZone == "Yukon Standard", TimeZone := "-9" ]
allStaionDT[, TimeZone := str_replace(TimeZone, "\\+", "")]

allStnNumColumns <- c("GroundHeight", "StationHeight", "BarometerHeight", "Latitude", "Longitude", "TimeZone")
allStaionDT <- UDFConvertFeaturesToNumeric(allStaionDT, allStnNumColumns)

# Let us make sure the conversion happened correctly
str(allStaionDT)
rm(allStnNumColumns)
```


**Merge allStation data to Train & Test data, once for Origin and again for Destination**
```{r}
orgColNames <- c()
dstColNames <- c()
for(col in colnames(allStaionDT)){
  orgColNames <- c(orgColNames, ifelse(col == "AirportID", "Origin", paste0(col, "_ORG")))
  dstColNames <- c(dstColNames, ifelse(col == "AirportID", "Destination", paste0(col, "_DST")))
}

trainDT <- UDFLeftOuterMergeDataTables(trainDT, allStaionDT, orgColNames)
trainDT <- UDFLeftOuterMergeDataTables(trainDT, allStaionDT, dstColNames)

testDT <- UDFLeftOuterMergeDataTables(testDT, allStaionDT, orgColNames)
testDT <- UDFLeftOuterMergeDataTables(testDT, allStaionDT, dstColNames)

#Remove transit variables to clear up space
rm(allStaionDT, col, orgColNames, dstColNames)
```




## Pre-Process, aggregate & Merge Weather Data

**There are many records in weather data which are not required, so lets filter only for weather station ids that are present in Train & Test**
```{r}

trainWeatherDT[["WeatherStationID"]] <- as.integer(trainWeatherDT[["WeatherStationID"]])
testWeatherDT[["WeatherStationID"]] <- as.integer(testWeatherDT[["WeatherStationID"]])

trainUniqueWSID <- unique(rbindlist(list(trainDT[, .(WeatherStationID_ORG)], trainDT[, .(WeatherStationID_DST)])))
trainWeatherDT <- UDFRightOuterMergeDataTables(trainWeatherDT, trainUniqueWSID, "WeatherStationID")

testUniqueWSID <- unique(rbindlist(list(testDT[, .(WeatherStationID_ORG)], testDT[, .(WeatherStationID_DST)])))
testWeatherDT <- UDFRightOuterMergeDataTables(testWeatherDT, testUniqueWSID, "WeatherStationID")

rm(trainUniqueWSID, testUniqueWSID)
```





**Convert Weather $ precipitation data columns to appropriate datatypes as per details provided in Attribute_Information.pdf** 
1. Visibility is numeric measured in statutet miles. Values has SM suffix so replace SM with blank and then convert
2. DBT is dry bulb temperature measured in whole degree celcius 
3. DewPointTemp is numeric measured in Degree celcius
4. RelativeHumidityPercent is numeric measured in percent
5. WindSpeed is numeric measured in knots.Some rows has special character "/", so replace it with blank before conversion
6. WindGustValue is maximum 5-sec peak wind speed measured
7. StationPressure is the pressure felt at that station or spot but not adjusted to an equivalent at sea level
8. Sky Condition is categorical

Note: WindDirection is given as numeric but Some values are "VRB" for WindDirection and by definition Variable Wind Direction may be reported in following instances: 
* Wind speed is 6 knots or less, "VRB" may be used for direction. 
* Wind direction varies by 60 degrees or more while average wind speed is greater than 6 knots.Example: 340V040 indicates wind variable between 340 and 040 degrees. Replacing VRB with 185 for now
  
```{r}
# Checking for any non numeric values using unique function so that conversion does not result in NA values

#unique(trainWeatherDT[, .(Visibility)][order(-Visibility)])
#unique(testWeatherDT[, .(Visibility)][order(-Visibility)])
#unique(trainWeatherDT[, .(DBT)][order(-DBT)])
#unique(testWeatherDT[, .(DBT)][order(-DBT)])
#unique(trainWeatherDT[, .(DewPointTemp)][order(-DewPointTemp)])
#unique(testWeatherDT[, .(DewPointTemp)][order(-DewPointTemp)])
#unique(trainWeatherDT[, .(RelativeHumidityPercent)][order(-RelativeHumidityPercent)])
#unique(testWeatherDT[, .(RelativeHumidityPercent)][order(-RelativeHumidityPercent)])
#unique(trainWeatherDT[, .(WindSpeed)][order(-WindSpeed)])
#unique(testWeatherDT[, .(WindSpeed)][order(-WindSpeed)])
#unique(trainWeatherDT[, .(WindDirection)][order(-WindDirection)])
#unique(testWeatherDT[, .(WindDirection)][order(-WindDirection)])
#unique(trainWeatherDT[, .(WindGustValue)][order(-WindGustValue)])
#unique(testWeatherDT[, .(WindGustValue)][order(-WindGustValue)])
#unique(trainWeatherDT[, .(StationPressure)][order(-StationPressure)])
#unique(testWeatherDT[, .(StationPressure)][order(-StationPressure)])

trainWeatherDT[!is.na(Visibility), Visibility := str_replace(Visibility, "SM", "")]
testWeatherDT[!is.na(Visibility), Visibility := str_replace(Visibility, "SM", "")]
trainWeatherDT[!is.na(WindSpeed), WindSpeed := str_replace(WindSpeed, "\\/", "")]
testWeatherDT[!is.na(WindSpeed), WindSpeed := str_replace(WindSpeed, "\\/", "")]
trainWeatherDT[WindDirection == "VRB", WindDirection := "185"]
testWeatherDT[WindDirection == "VRB", WindDirection := "185"]

```





**Convert Train Weather data features to appropriate data types**
```{r}
weatherDataNumColumns <- c("Visibility", "DBT", "DewPointTemp", "RelativeHumidityPercent", "WindSpeed", "WindDirection", "WindGustValue", "StationPressure")

print("Train NA Counts before converstion")
colSums(is.na(trainWeatherDT))

trainWeatherDT <- UDFConvertFeaturesToNumeric(trainWeatherDT, weatherDataNumColumns)

print("Train NA Counts after converstion")
colSums(is.na(trainWeatherDT))
```


**Convert Test weather data features to appropriate data types**
```{r}
print("Test NA Counts before converstion")
colSums(is.na(testWeatherDT))

testWeatherDT <- UDFConvertFeaturesToNumeric(testWeatherDT, weatherDataNumColumns)

print("Test NA Counts after converstion")
colSums(is.na(testWeatherDT))
rm(weatherDataNumColumns)
```


**Aggregate Train Weather data for same WeatherStationID & RecordedTime Rounded to Nearest hour**
```{r}
trainWeatherAggDT <- trainWeatherDT[, .(SkyConditions = unique(SkyConditions, na.rm = T)[1],
                                        Visibility = round(mean(Visibility, ), 2),
                                        DBT = round(mean(DBT, na.rm=T), 2),
                                        DewPointTemp = round(mean(DewPointTemp, na.rm=T), 2),
                                        RelativeHumidityPercent = round(mean(RelativeHumidityPercent, na.rm=T), 2),
                                        WindSpeed = round(mean(WindSpeed, na.rm=T), 2),
                                        WindDirection = round(mean(WindDirection, na.rm=T), 2),
                                        WindGustValue = round(mean(WindGustValue, na.rm=T), 2),
                                        StationPressure = round(mean(StationPressure, na.rm=T), 2)),
                                    by = c("WeatherStationID", "RecordedTimeToNearestHour")]


trainWeatherAggDT[is.nan(Visibility), Visibility := NA]
trainWeatherAggDT[is.nan(DBT), DBT := NA]
trainWeatherAggDT[is.nan(DewPointTemp), DewPointTemp := NA]
trainWeatherAggDT[is.nan(RelativeHumidityPercent), RelativeHumidityPercent := NA]
trainWeatherAggDT[is.nan(WindSpeed), WindSpeed := NA]
trainWeatherAggDT[is.nan(WindDirection), WindDirection := NA]
trainWeatherAggDT[is.nan(WindGustValue), WindGustValue := NA]
trainWeatherAggDT[is.nan(StationPressure), StationPressure := NA]

rm(trainWeatherDT)
```




**Aggregate Test Weather data for same WeatherStationID & RecordedTime Rounded to Nearest hour**
```{r}
testWeatherAggDT <- testWeatherDT[, .(SkyConditions = unique(SkyConditions, na.rm = T)[1],
                                      Visibility = round(mean(Visibility, na.rm=T), 2),
                                      DBT = round(mean(DBT, na.rm=T), 2),
                                      DewPointTemp = round(mean(DewPointTemp, na.rm=T), 2),
                                      RelativeHumidityPercent = round(mean(RelativeHumidityPercent, na.rm=T), 2),
                                      WindSpeed = round(mean(WindSpeed, na.rm=T), 2),
                                      WindDirection = round(mean(WindDirection, na.rm=T), 2),
                                      WindGustValue = round(mean(WindGustValue, na.rm=T), 2),
                                      StationPressure = round(mean(StationPressure, na.rm=T), 2)),
                                  by = c("WeatherStationID", "RecordedTimeToNearestHour")]

testWeatherAggDT[is.nan(Visibility), Visibility := NA]
testWeatherAggDT[is.nan(DBT), DBT := NA]
testWeatherAggDT[is.nan(DewPointTemp), DewPointTemp := NA]
testWeatherAggDT[is.nan(RelativeHumidityPercent), RelativeHumidityPercent := NA]
testWeatherAggDT[is.nan(WindSpeed), WindSpeed := NA]
testWeatherAggDT[is.nan(WindDirection), WindDirection := NA]
testWeatherAggDT[is.nan(WindGustValue), WindGustValue := NA]
testWeatherAggDT[is.nan(StationPressure), StationPressure := NA]

rm(testWeatherDT)
```



**Merge Aggregated Weather Data with respective Train & Test data**
1. First merge for origin
2. Again merge for destination
```{r}
orgWeatherColNames <- c()
dstWeatherColNames <- c()
for(col in colnames(trainWeatherAggDT)){
  orgWeatherColNames <- c(orgWeatherColNames, paste0(col, "_ORG"))
  dstWeatherColNames <- c(dstWeatherColNames, paste0(col, "_DST"))
}

trainDT <- UDFLeftOuterMergeDataTables(trainDT, trainWeatherAggDT, orgWeatherColNames)
trainDT <- UDFLeftOuterMergeDataTables(trainDT, trainWeatherAggDT, dstWeatherColNames)

testDT <- UDFLeftOuterMergeDataTables(testDT, testWeatherAggDT, orgWeatherColNames)
testDT <- UDFLeftOuterMergeDataTables(testDT, testWeatherAggDT, dstWeatherColNames)

rm(col, orgWeatherColNames, dstWeatherColNames, trainWeatherAggDT, testWeatherAggDT)
```




## Pre-Process, aggregate & Merge Precipitation Data 
**There are many records in Precipitation data that are not required, so lets filter only for weather station ids that are present in Train & Test**
```{r}
trainUniqueWSID <- unique(rbindlist(list(trainDT[, .(WeatherStationID_ORG)], trainDT[, .(WeatherStationID_DST)])))
trainPrecipDT <- UDFRightOuterMergeDataTables(trainPrecipDT, trainUniqueWSID, "WeatherStationID")

testUniqueWSID <- unique(rbindlist(list(testDT[, .(WeatherStationID_ORG)], testDT[, .(WeatherStationID_DST)])))
testPrecipDT <- UDFRightOuterMergeDataTables(testPrecipDT, testUniqueWSID, "WeatherStationID")

rm(trainUniqueWSID, testUniqueWSID)
```



**Convert Train Precipitation features to appropriate data types**
```{r}
print("Train NA Counts before converstion")
colSums(is.na(trainPrecipDT))
trainPrecipDT[["HourlyPrecip"]] <- as.numeric(trainPrecipDT[["HourlyPrecip"]])
print("Train NA Counts after converstion")
colSums(is.na(trainPrecipDT))
```


**Convert Test Precipitation features to appropriate data types**
```{r}
print("Test NA Counts before converstion")
colSums(is.na(testPrecipDT))
testPrecipDT[["HourlyPrecip"]] <- as.numeric(testPrecipDT[["HourlyPrecip"]])
print("Test NA Counts after converstion")
colSums(is.na(testPrecipDT))
```



**Aggregate Precipitation data for same WeatherStationID & RecordedTimeToNearestHour**
```{r}
#Aggregation for train precip data
trainPrecipAggDT <- trainPrecipDT[, .(HourlyPrecip = round(mean(HourlyPrecip, na.rm=T), 2)),
                                    by = c("WeatherStationID", "RecordedTimeToNearestHour")]
trainPrecipAggDT[is.nan(HourlyPrecip), HourlyPrecip := NA]

#Aggreagation for test precip data
testPrecipAggDT <- testPrecipDT[, .(HourlyPrecip = round(mean(HourlyPrecip, na.rm=T), 2)),
                                    by = c("WeatherStationID", "RecordedTimeToNearestHour")]
testPrecipAggDT[is.nan(HourlyPrecip), HourlyPrecip := NA]

rm(trainPrecipDT, testPrecipDT)
```


**Merge Aggregated Precipitation Data with respective Train & Test data**  
1. First merge for origin
2. Again merge for destination
```{r}
orgPrecipColNames <- c()
dstPrecipColNames <- c()
for(col in colnames(trainPrecipAggDT)){
  orgPrecipColNames <- c(orgPrecipColNames, paste0(col, "_ORG"))
  dstPrecipColNames <- c(dstPrecipColNames, paste0(col, "_DST"))
}

trainDT <- UDFLeftOuterMergeDataTables(trainDT, trainPrecipAggDT, orgPrecipColNames)
trainDT <- UDFLeftOuterMergeDataTables(trainDT, trainPrecipAggDT, dstPrecipColNames)

testDT <- UDFLeftOuterMergeDataTables(testDT, testPrecipAggDT, orgPrecipColNames)
testDT <- UDFLeftOuterMergeDataTables(testDT, testPrecipAggDT, dstPrecipColNames)

rm(col, orgPrecipColNames, dstPrecipColNames, trainPrecipAggDT, testPrecipAggDT)
```



# Convert Features to appropriate Data Types



```{r}
columnsToGroupByOrg <- c("Origin", "RecordedTimeToNearestHour_ORG")
columnsToGroupByDest <- c("Destination", "RecordedTimeToNearestHour_DST")
columnsToMergeOrg <- c("AirportId", "RecordedTimeToNearestHour", "Departing")
columnsToMergeDest <- c("AirportId", "RecordedTimeToNearestHour", "Arriving")

DepartingFlights <- trainDT[, .(Departing = .N), by = columnsToGroupByOrg]
colnames(DepartingFlights) <- columnsToMergeOrg
ArrivingFlights <- trainDT[, .(Arriving = .N), by = columnsToGroupByDest]
colnames(ArrivingFlights) <- columnsToMergeDest

DepartingArrivingFlights <- merge(DepartingFlights, ArrivingFlights, 
                               by = base::intersect(names(DepartingFlights), names(ArrivingFlights)), all = T)

DepartingArrivingFlights[is.na(Departing), Departing := 0]
DepartingArrivingFlights[is.na(Arriving), Arriving := 0]

trainDT <- UDFLeftOuterMergeDataTables(trainDT, DepartingArrivingFlights, 
                                       c(columnsToGroupByOrg, "FlightsFromOrigin", "FlightsToOrigin"))

trainDT <- UDFLeftOuterMergeDataTables(trainDT, DepartingArrivingFlights, 
                                       c(columnsToGroupByDest, "FlightsFromDestination", "FlightsToDestination"))

trainDT[, FlightsInOrigin := (FlightsFromOrigin+FlightsToOrigin)]
trainDT[, FlightsInDestination := (FlightsFromDestination+FlightsToDestination)]

trainDT[, c("FlightsFromOrigin", "FlightsToOrigin", "FlightsFromDestination", "FlightsToDestination") := NULL]

rm(DepartingFlights, ArrivingFlights, DepartingArrivingFlights)
```

**Repeating above step for test**
```{r}
DepartingFlights <- testDT[, .(Departing = .N), by = columnsToGroupByOrg]
colnames(DepartingFlights) <- columnsToMergeOrg
ArrivingFlights <- testDT[, .(Arriving = .N), by = columnsToGroupByDest]
colnames(ArrivingFlights) <- columnsToMergeDest

DepartingArrivingFlights <- merge(DepartingFlights, ArrivingFlights, 
                                  by = base::intersect(names(DepartingFlights), names(ArrivingFlights)), all = T)

DepartingArrivingFlights[is.na(Departing), Departing := 0]
DepartingArrivingFlights[is.na(Arriving), Arriving := 0]

testDT <- UDFLeftOuterMergeDataTables(testDT, DepartingArrivingFlights, 
                                       c(columnsToGroupByOrg, "FlightsFromOrigin", "FlightsToOrigin"))

testDT <- UDFLeftOuterMergeDataTables(testDT, DepartingArrivingFlights, 
                                       c(columnsToGroupByDest, "FlightsFromDestination", "FlightsToDestination"))

testDT[, FlightsInOrigin := (FlightsFromOrigin+FlightsToOrigin)]
testDT[, FlightsInDestination := (FlightsFromDestination+FlightsToDestination)]

testDT[, c("FlightsFromOrigin", "FlightsToOrigin", "FlightsFromDestination", "FlightsToDestination") := NULL]

rm(DepartingFlights, ArrivingFlights, DepartingArrivingFlights)
rm(columnsToGroupByOrg, columnsToGroupByDest, columnsToMergeOrg, columnsToMergeDest)
```


*Month, DayOfWeek & DayofMonth are categorical, using lubridate package converting to categorical values
```{r}
trainDT[, Month := month(ScheduledDepDateTime, label = TRUE)]
trainDT[, DayOfWeek := wday(ScheduledDepDateTime, label = TRUE)]
trainDT[, DepHour:= hour(ScheduledDepDateTime)]
trainDT[, DepMin:= minute(ScheduledDepDateTime)]
trainDT[, ArrHour:= hour(ScheduledArrDateTime)]
trainDT[, ArrMin:= minute(ScheduledArrDateTime)]

testDT[, Month := month(ScheduledDepDateTime, label = TRUE)]
testDT[, DayOfWeek := wday(ScheduledDepDateTime, label = TRUE)]
testDT[, DepHour:= hour(ScheduledDepDateTime)]
testDT[, DepMin:= minute(ScheduledDepDateTime)]
testDT[, ArrHour:= hour(ScheduledArrDateTime)]
testDT[, ArrMin:= minute(ScheduledArrDateTime)]

hourInterval <- seq(0, 24, 2)
trainDT[, DepHourBin:= findInterval(DepHour, hourInterval)]
trainDT[, ArrHourBin:= findInterval(ArrHour, hourInterval)]
testDT[, DepHourBin:= findInterval(DepHour, hourInterval)]
testDT[, ArrHourBin:= findInterval(ArrHour, hourInterval)]

minuteInterval <- seq(0, 60, 10)
trainDT[, DepMinBin:= findInterval(DepMin, minuteInterval)]
trainDT[, ArrMinBin:= findInterval(ArrMin, minuteInterval)]
testDT[, DepMinBin:= findInterval(DepMin, minuteInterval)]
testDT[, ArrMinBin:= findInterval(ArrMin, minuteInterval)]


trainDT[["FlightDelayStatus"]] <- as.factor(trainDT[["FlightDelayStatus"]])
catColumns <- c("Destination", "Origin", "Month", "DayofMonth", "DayOfWeek", "DepHourBin", "DepMinBin", "ArrHourBin", "ArrMinBin")
trainDT <- UDFConvertFeaturesToFactor(trainDT, catColumns)
testDT <- UDFConvertFeaturesToFactor(testDT, catColumns)

rm(catColumns, hourInterval, minuteInterval)
```

**Drop Features that are not required**
1. FlightNumber is an id column with unique values so not required
2. WeatherStationID columns are ids for Origin & Destination hence not required
3. RecordedTimeToNearestHour columns are derived columns to help with merging weather data, so not required after merging
4. ScheduledDepDateTime & ScheduledArrDateTime are not required as required information from dates has been already extracted

```{r}
columsToDrop <- c("FlightNumber", "WeatherStationID_ORG", "WeatherStationID_DST", "RecordedTimeToNearestHour_ORG", "RecordedTimeToNearestHour_DST", "ScheduledDepDateTime", "ScheduledArrDateTime", "DepHour", "ArrHour", "DepMin", "ArrMin")

trainDT[, c(columsToDrop) := NULL]
testDT[, c(columsToDrop) := NULL]

rm(columsToDrop)
```
  

**Save Merged train & test files for future reference**
```{r}
write.csv(trainDT, "TrainAggMerged.csv", row.names = F)
write.csv(testDT, "TestAggMerged.csv", row.names = F)
```




